---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The premise of `phrasenets` is very simple: to help you build "phrase nets." These are very easy, in fact, if you know your way around you probably won't need this package at all.

## What are "phrase nets"

It's almost too simple, it connects words according to "connectors" of your choosing, e.g.:

- "A to B"
- "A and B"
- "B at C"

The default connectors are `to`, `in`, `at`, `and`, and `of`.

# Examples

The `phrase_net` function simply returns a lsit of edges and the number of times these were found in the body of text.

```{r setup}
library(phrasenets)

data(reuters)

phrase_net(reuters, text = text) %>% 
  head() %>% 
  knitr::kable()
```

The package also comes with a convenience function `filter_net` to filter out any edges that contains specific words. Below we remove edges with `the` and `a` and use the `plot_sigmajs` to easily plot the network using [sigmajs](http://sigmajs.john-coene.com/).

```{r}
reuters %>% 
  phrase_net(text = text) %>% 
  filter_net(c("a", "the")) %>% 
  dplyr::filter(occurences > 5) %>% 
  plot_sigmajs()
```

The dataset provided (`reuters`) contains articles on 10 difference commodities, let's plot their respective phrasenets.

```{r, fig.width=9,fig.height=12}
library(dplyr)
library(purrr)
library(ggraph)
library(tidygraph)

# create a graph for each commodity
subgraphs <- reuters %>% 
  group_split(category) %>% 
  map(phrase_net, text = text) %>% 
  map(filter_net, c("a", "the")) %>% 
  map(filter, occurences > 1) %>% 
  map(as_tbl_graph) %>% 
  map(function(x){
    mutate(x, size = centrality_degree())
  })

plot_it <- function(g, commodity){
  ggraph(g, layout = 'kk') + 
    geom_edge_fan(show.legend = FALSE) + 
    geom_node_point(aes(size = size, colour = size), show.legend = FALSE) + 
    theme_graph(
      background = "#f9f7f1"
    ) +
    labs(caption = tools::toTitleCase(commodity))
} 

commodities <- unique(reuters$category)

map2(subgraphs, commodities, plot_it) %>% 
  patchwork::wrap_plots(ncol = 2) &
  theme(
    panel.background = element_rect(fill = "#f9f7f1"),
    plot.background = element_rect(fill = "#f9f7f1")
  )
```